---
title: "Sobol - Variance-based sensitivty analysis"
output: 
  html_notebook: 
    code_folding: none
    theme: cosmo
---

Sensitivity analysis can be broadly categorized into local sensitivity analysis and global sensitivity analysis. Local sensitivity analysis, that is, normally known as one-at-a-time (OAT) measure, is carried out by varying single input parameters of interest and keeping other parameters at constant value in order 
to study model output. 

An alternative to local sensitivity analysis is the global sensitivity analysis, of which there are several varieties ranging from a qualitative screening method to quantitative technique (Sobol’ 1990; Morris 1991; Campolongo et al. 2007).
The global sensitivity analysis provides a better coverage of input spaces, more informative indicators than the local sensitivity tool, and was able to provide statistical description on the model outputs.

## Sobol sensitivity analysis in R
[Water programming group](https://waterprogramming.wordpress.com/2012/09/19/starting-out-with-the-r-sensitivity-package/)

&nbsp;

We first start by loading sobol package
```{r}
library("sensitivity")
```
&nbsp;

Next, create two random samples (n rows x 8 columns each)
```{r}
n<-1000
X1<-data.frame(matrix(runif(8*n), nrow=n))
X2<-data.frame(matrix(runif(8*n), nrow=n))
```
&nbsp;

Apply sobol function:
We only want to perform sampling, so the model is NULL.
```{r}
sa<-sobol2002(model=NULL, X1, X2, nboot=10)
```
&nbsp;

Write results to a file
```{r}
write(t(sa$X), file="test.samples", 8)
```


