---
title: "Alluvial Plots"
output:
  html_document: default
  html_notebook: default
---

Alluvial plots work similarly to parallel coordinates plots, but instead of having ranges of values in the axes, it contains bins whose sizes in an axis depends on how many data points belong to that bin. Data points that fall within the same categories in all axes are grouped into alluvia (stripes), whose thicknesses reflect the number of data points in each alluvium.

Load alluvial package & dataset
```{r, echo = TRUE, message= FALSE}
library(magrittr) 
library(dplyr) 
library(alluvial)
tit <- tibble::as_data_frame(Titanic)
tit %>% head() %>% knitr::kable()
```

Generate Alluvial plot
```{r, echo = TRUE}
alluvial(
  # Data frame to be plotted
  select(tit, Survived, Sex, Age, Class),
  # numeric, vector of frequencies of the same length as the number of observations
  freq =tit$n,
  # vector of colors of the stripes
  col = ifelse(tit$Survived == "Yes", "orange", "grey"),
  #vector of border colors for the stripes
  border = ifelse(tit$Survived == "Yes", "orange", "grey"),
  #vector of border colors for the stripes
  layer = tit$Survived != "Yes",
  #numeric, vector of transparency of the stripes
  alpha = 0.8,
  #logical, whether to use blocks to tie the flows together at each category
  blocks = TRUE
)
```

